---
title: Thin Data
output: 
  revealjs::revealjs_presentation:
    theme: black
    transition: none
    center: false
---

```{r include = FALSE}
library(knitr)
library(kableExtra)
library(tidyverse)

knitr::opts_chunk$set(
    echo = FALSE
  , warning = FALSE
)
```

# What is thin data? 

## What is thin data

Thin data is everything that big data isn't.

Thin data is:

- Collected rarely (quarterly, annually)
- Short (fewer than 50 observations)
- Possibly wide (overspecified)

##

##

##

# Mitigation

## Mitigation

```{r }
tribble(
    ~Method, ~Description
  , 'Case control study', 'Identify exemplary cases and work backwords'
  , 'Bootstrap', 'Sample with replacement'
  , 'Bayes', 'Alter a distribution based on data and prior judgment'
  , 'Penalized regression', 'Restrict the number and/or influence of parameters') %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

# Case control study

## CCS

Stuff

# Bootstrap

## Bootstrap

Stuff

# Bayes

## Bayes

Mama weer all Bayezee now

# Penalized regression

## Penalized regresssion

What is the L2 norm

## Lasso

## Ridge

# Conclusion